---
title: "Analysis_TOJ_Flow"
output: html_notebook
---


1.0 Install Packages
```{r}
install.packages("pacman")

pacman::p_load(lme4, nlme, tidyverse, lmerTest, gridExtra, ggplot2, ggthemes, dplyr, sjstats, texreg, sjmisc, sjlabelled, sjPlot, devtools, brms, bayesplot, devtools, ggeffects, texreg, xtable, ggeffects)
```



2.0 Hierarchical linear models
2.1 Hierarchical linear models for the difference of the "just noticeable difference" (JND)

2.1.0 load, prepare data for JND-models and defining nominal variables as factors

```{r}
data(withoutJND)

hlmjnddata <-withoutJND %>% mutate(subject = as.factor(vpn), session = as.factor(session), prepost = as.factor(pre0post1), condition = as.factor(endo0exo1), domain = as.factor(m0a1))%>%
  select(subject, flow, session, condition, JND, prepost, condition, domain, control)

#rescaling "flow"

hlmjnddata$cflow<-scale(hlmjnddata$flow, scale = FALSE) # grand mean center the variable
names(hlmjnddata)
```


2.1.1 Fully unconditional model

```{r}
m0.subject<- lmer(JND ~ (1|subject), hlmjnddata , REML = FALSE)
m0.session<- lmer(JND ~ (1|subject/session), hlmjnddata , REML = FALSE)

summary(m0.session)
```


2.1.1.1 Explained Variance by each Level

```{r}
#level 3
132.6/(132.6+330.3+397.9) = 0.1540428

#level 2 
330.3/(132.6+330.3+397.9) = 0.3837128

#level 1
397.9/(132.6+330.3+397.9) = 0.4622444

#Graphical indices

boxplot(JND ~ subject, data = hlmjnddata)
boxplot(JND ~ subject/session, data = hlmjnddata)

```


2.1.1.2 Means, distribution of the variables and cronbachs alpha of the nine subscales

```{r}
###### Cronbachs Alpha & Mean for Subscales ######
install.packages("psych")

library(psych)



df = cronbachs_alpha[,!(names(cronbachs_alpha) %in% c("File"))]

## Creating Subscales
my.keys <- list(CG = c("Q1", "Q2", "Q3"),co = c("Q4", "Q5", "Q6", "Q7"),UF = c("Q8", "Q9"),CS = c("Q10", "Q11", "Q12"),CN = c("Q13", "Q14"),SC = c("Q15", "Q16", "Q17"),AE = c("Q18", "Q19", "Q20"),MAA= c("Q22", "Q23", "Q26"),TT = c("Q21", "Q24", "Q25"))
    my.scales <- scoreItems(my.keys,df)
    my.scores <- my.scales$scores
    my.scores
                                      
    describe(my.scores)
    my.scales                                          
                                          

                                      
## Cronbachs Alpha ##
   
    my.scales  
    
## Deeper Cronbachs Alpha Analysis
         
data(cronbachs_alpha)
alpha(cronbachs_alpha, check.keys=F)

## CG = clear goals

alpha(cronbachs_alpha[c("Q1", "Q2", "Q3")], check.keys=F)

##CO = concentration on task at hand;

alpha(cronbachs_alpha[c("Q4", "Q5", "Q6", "Q7")], check.keys=F)


## UF = unambiguous feedback

alpha(cronbachs_alpha[c("Q8", "Q9")], check.keys=F)


##CS = challenge skill balance

alpha(cronbachs_alpha[c("Q10", "Q11", "Q12")], check.keys=F)


##CN = sense of control

alpha(cronbachs_alpha[c("Q13", "Q14")], check.keys=F)


## SC = Loss of self-consciousness

alpha(cronbachs_alpha[c("Q15", "Q16", "Q17")], check.keys=F)


## AE = autotelic experience.

alpha(cronbachs_alpha[c("Q18", "Q19", "Q20")], check.keys=F)


## MAA = merging actions and awareness

alpha(cronbachs_alpha[c("Q22", "Q23", "Q26")], check.keys=F)


## TT = transformation of time;

alpha(cronbachs_alpha[c("Q21", "Q24", "Q25")], check.keys=F)


##Distribution

plot(density(hlmjnddata$cflow))
plot(density(hlmjnddata$JND))
shapiro.test(hlmjnddata$cflow)
shapiro.test(hlmjnddata$JND)


#Testing for normal distribution
qqnorm(resid(m0.session)) + 
qqline(resid(m0.session)) 
#There is some deviation from from the expected normal line towards the tails, but overall the line looks straight and therefore pretty normal and suggests that the assumption is not violated.


```


2.1.2 Pre/post as only predictor

```{r}
m1.jnd_prepost<- lmer(JND ~ prepost + (1|subject/session), hlmjnddata , REML = FALSE)
m1.jnd_prepost_slope<- lmer(JND ~ prepost + (prepost|subject/session), hlmjnddata , REML = FALSE, control = lmerControl(optimizer ="Nelder_Mead"))

```


2.1.2.1 Anova M0 vs pre/post-models

```{r}
anova(m0.session, m1.jnd_prepost, m1.jnd_prepost_slope )
```


2.1.3 Condition as predictor

```{r}
m1.jnd_endoexo<- lmer(JND ~ prepost + condition + (1|subject/session), hlmjnddata , REML = FALSE)
m1.jnd_endoexo_slope<- lmer(JND ~ prepost + condition + (1|subject/session) + (condition|subject), hlmjnddata , REML = FALSE, control = lmerControl(optimizer ="Nelder_Mead"))

```


2.1.3.1  Anova pre/post-model vs condition-model

```{r}
anova(m1.jnd_prepost, m1.jnd_endoexo, m1.jnd_endoexo_slope)
```


2.1.4 Flow as a predictor in the interaction with pre/post measurements

```{r}
m1.jnd_flow<- lmer(JND ~ prepost*cflow + condition + (1|subject/session), hlmjnddata , REML = FALSE)
m1.jnd_flow_rnd<- lmer(JND ~ prepost*cflow + condition + (cflow|subject/session), hlmjnddata , REML = FALSE,  control = lmerControl(optimizer ="Nelder_Mead"))
m1.jnd_flow_con<- lmer(JND ~ prepost*cflow * condition + (cflow|subject/session), hlmjnddata , REML = FALSE,  control = lmerControl(optimizer ="Nelder_Mead"))

summary(m1.jnd_flow)
summary(m1.jnd_flow_rnd)
summary(m1.jnd_flow_con)
confint(m1.jnd_flow_rnd, oldNames=F)

tab_model(m1.jnd_flow, show.se = 1, show.obs=1, show.ngroups=0) #html-table
texreg(m1.jnd_flow, ci.force=T, se.force=T, pvalues.force=T) #Latex-table
xtable(coef(summary(m1.jnd_flow))) #Latex-table

```


2.1.4.1 Anova flow-model vs condition-model

```{r}
anova(m1.jnd_endoexo, m1.jnd_flow)
```


2.1.5 Domain as a predictor

```{r}
m1.jnd_domain<- lmer(JND ~ domain + (1|subject/session), hlmjnddata , REML = FALSE)
m1.jnd_domain_prepost<- lmer(JND ~ domain*prepost + (1|subject/session), hlmjnddata , REML = FALSE)

summary(m1.jnd_domain)
summary(m1.jnd_domain_prepost)
```


2.1.6 Influence of the control question on the interaction of pre/post and flow regardig to JND

```{r}
m1.jnd_flow_control<- lmer(JND ~ prepost*cflow * control+ (1|subject/session), hlmjnddata , REML = FALSE)

summary(m1.jnd_flow_control)
```


2.2 Bayesian HLM of the JND

```{r}
m2.jnd_session_b<- brm(JND ~ (1|subject/session), hlmjnddata,  iter = 4000)
m3.jnd_prepost_b<- brm(JND ~ prepost + (1|subject/session), hlmjnddata,  iter = 4000)
m3.jnd_condition_b<- brm(JND ~ prepost*cflow + condition + (1|subject/session), hlmjnddata,  iter = 4000)
m3.jnd_flow_b<- brm(JND ~ prepost*cflow + condition + (1|subject/session), hlmjnddata,  iter = 4000)

saveRDS(m2.jnd_session_b, file = "m2.jnd_session_b.rds")
saveRDS(m3.jnd_prepost_b, file = "m3.jnd_prepost_b.rds")
saveRDS(m3.jnd_condition_b, file = "m3.jnd_condition_b.rds")
saveRDS(m3.jnd_flow_b, file = "m3.jnd_flow_b.rds")

summary(m3.jnd_flow_b)
tab_model(m3.jnd_flow_b, show.se = T)
```


2.2.1 Bayesian models comparison

```{r}
loo1<-LOO(m2.jnd_session_b, reloo=1)
loo2<-LOO(m3.jnd_prepost_b, reloo=1)
loo3<-LOO(m3.jnd_condition_b, reloo=1)
loo4<-LOO(m3.jnd_flow_b, reloo=1)

loo::compare(loo1, loo2, loo3, loo4)
```


2.2.2 Histogram of posterior samples of M3b_JND

```{r}
m3.jnd_flow_b %>%
  plot( 
    combo = c("hist", "trace"), widths = c(1, 1.5),
  theme = theme_bw(base_size = 10)
)    

```


2.2.3 Figure of the effects of M3b_JND

```{r}
# create df for plotting
summary_df <- ggpredict(m3.jnd_flow_b, c("cflow", "prepost"), )

# define gray colors for the groups (pre; post)
colours <- c("Black","Black") # for greyscale: #a8a7a7; #383838

  x<-ggplot(summary_df,aes(x=x,y=predicted))+
    geom_line(aes(color=group,linetype=group),
              size=1.2)+ # change inner line size
    geom_ribbon(aes(ymin = summary_df$conf.low, ymax = summary_df$conf.high,fill = group,colour = group),labels = c("Pre", "Post"), linetype = 0,alpha = 0.07)+ # produces conf. ribbons
    labs(fill='Pre/Post') +
     labs(color='Pre/Post') +
    labs(linetype='Pre/Post')+
    scale_y_continuous(limits = c(30,75))+ # define y-axis limits
    theme_tufte(base_family = "GillSans")+ # make the plot tufte
    ylab("JND")+ # y-axis label
    xlab("Flow")+ # x-axis label
    theme(axis.line = element_line(size = .5, color = "#969696"), # more plot aesthetics changes
          axis.ticks = element_line(color = "#969696"),
          axis.text.x = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          text=element_text(size = 16),
          plot.title = element_text(size =18,
                                    hjust = 0.5),
          axis.title.y = element_text(vjust = 0.5,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)))+
    scale_colour_manual(values=colours, labels = c("Pre", "Post")) + # apply defined colors
    scale_fill_manual(values=colours, labels = c("Pre", "Post"))
  
show(x)

ggsave("Figure-05.jpeg", plot = last_plot(), dpi = 900)
```


2.2.4 Plotting the differences of the estimated bayesian and frequentistic Model of the JND

```{r}
Ploteffects_JND <-Compare_Models_JND %>% 
  select(lCI, uCI, Mean, Parameter=Parameters, Model)

apatheme=theme_bw()+  #Creating APA conform Theme  
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text=element_text(),
        legend.title=element_blank())

a <- ggplot() + 
  geom_errorbarh(data=Ploteffects_JND, mapping=aes(y=Parameter, xmin=lCI, xmax=uCI, colour=Model, height=0.4)) +
  geom_point(data=Ploteffects_JND, mapping=aes(y=Parameter, x=Mean, colour=Model), size=2)

Plott_dif_Models_JND <- a  + apatheme + geom_vline(xintercept = 0, linetype = "dotted") #Adding theme and lino on 0

show(Plott_dif_Models_JND) 
```






2.3 Hierarchical linear models for the difference of the "point of subjective simultaneity" (PSS)

2.3.0 load, prepare data for PSS-models and defining nominal variables as factors

```{r}
data(withoutPSS)
hlmpssdata <-withoutPSS %>% mutate(subject = as.factor(vpn), session = as.factor(session), prepost = as.factor(pre0post1), condition = as.factor(endo0exo1),  domain = as.factor(m0a1))%>%
  select(subject, flow, session, condition, PSS = posdisPSS, prepost, condition, domain, control)

hlmpssdata$cflow<-scale(hlmpssdata$flow, scale = FALSE) # grand mean center flow
```


2.3.1 Fully unconditional model

```{r}
m0.pss_subject<- lmer(PSS ~ (1|subject), hlmpssdata , REML = FALSE)
m0.pss_session<- lmer(PSS ~ (1|subject/session), hlmpssdata , REML = FALSE)

summary(m0.pss_subject)
```


2.3.1.1 Explained Variance by each Level

```{r}
# Intraclass Correlation Coefficient (ICC) of m0.subject
performance::icc(m0.pss_subject)

boxplot(PSS ~ subject, data = hlmpssdata)
boxplot(PSS ~ subject/session, data = hlmpssdata)

```


2.3.1.2 Normal distribution of the variabls

```{r}
plot(density(hlmpssdata$cflow))
plot(density(hlmpssdata$PSS))
shapiro.test(hlmpssdata$cflow)
shapiro.test(hlmpssdata$PSS)


#Testing for normal distribution
qqnorm(resid(m0.pss_subject))
qqline(resid(m0.pss_subject)) 
#There is some deviation from from the expected normal line towards the tails, but overall the line looks straight and therefore pretty normal and suggests that the assumption is not violated.


```


2.3.2 Pre/post as only predictor

```{r}
m1.pss_prepost<- lmer(PSS ~ prepost + (1|subject), hlmpssdata , REML = FALSE)
m1.pss_prepost_slope<- lmer(PSS ~ prepost + (prepost|subject), hlmpssdata , REML = FALSE, control = lmerControl(optimizer ="Nelder_Mead"))

summary(m1.pss_prepost)
```


2.3.2.1 Anova M0 vs pre/post-model

```{r}
anova(m0.pss_subject, m1.pss_prepost)
```


2.3.3 Condition as predictor

```{r}
m1.pss_endoexo<- lmer(PSS ~  condition + (1|subject), hlmpssdata , REML = FALSE, control = lmerControl(optimizer ="Nelder_Mead"))
m1.pss_endoexo_slope<- lmer(PSS ~  condition + (condition|subject), hlmpssdata , REML = FALSE, control = lmerControl(optimizer ="Nelder_Mead"))
```


2.3.3.1  Anova pre/post-model vs condition-model

```{r}
anova(m0.pss_subject, m1.pss_endoexo, m1.pss_endoexo_slope)
```


2.3.4 Flow as a predictor in the interaction with pre/post measurements

```{r}
m1.pss_flow<- lmer(PSS ~ prepost*cflow + condition + (condition|subject), hlmpssdata , REML = FALSE)
m1.pss_flow_rnd<- lmer(PSS ~ prepost*cflow + condition + (prepost*flow|subject), hlmpssdata , REML = FALSE)
m1.pss_flow_con<- lmer(PSS ~ prepost*cflow*condition + (condition|subject), hlmpssdata , REML = FALSE,  control = lmerControl(optimizer ="Nelder_Mead"))

tab_model(m1.pss_flow, show.se = 1, show.obs=1, show.ngroups=0) # html table
texreg(m1.pss_flow, ci.force=T, se.force=T, pvalues.force=T)  #latex table 1
xtable(coef(summary(m1.pss_flow)))  #latex table 2
```


2.3.4.1 Anova flow-model vs condition-model

```{r}
anova(m1.pss_endoexo_slope, m1.pss_flow, m1.pss_flow_rnd, m1.pss_flow_con)
```


2.3.5 Domain as a predictor

```{r}
m1.pss_domain<- lmer(PSS ~ domain + (1|subject), hlmpssdata , REML = FALSE)
m1.pss_domain_prepost<- lmer(PSS ~ domain*prepost + (1|subject), hlmpssdata , REML = FALSE)

summary(m1.pss_domain)
summary(m1.pss_domain_prepost)
```


2.3.6 Influence of the control question on the interaction of pre/post and flow regardig to PSS

```{r}
m1.pss_flow_control<- lmer(PSS ~ prepost*cflow * control+ (1|subject/session), hlmpssdata , REML = FALSE)

summary(m1.pss_flow_control)
```


2.4 Bayesian HLM of the PSS

```{r}
m2.pss_session_b<- brm(PSS ~ (1|subject), hlmpssdata,  iter = 4000)
m3.pss_prepost_b<- brm(PSS ~ prepost + (1|subject), hlmpssdata,  iter = 4000)
m3.pss_condition_b<- brm(PSS ~ condition + (1|subject), hlmpssdata,  iter = 4000)
m3.pss_condition_rnd_b<- brm(PSS ~ condition + (condition|subject), hlmpssdata,  iter = 4000)
m3.pss_flow_b<- brm(PSS ~ prepost*cflow + condition + (condition|subject), hlmpssdata,  iter = 4000)

saveRDS(m2.pss_session_b, file = "m2.pss_session_b.rds")
saveRDS(m3.pss_prepost_b, file = "m3.pss_prepost_b.rds")
saveRDS(m3.pss_condition_b, file = "m3.pss_condition_b.rds")
saveRDS(m3.pss_condition_rnd_b, file = "m3.pss_condition_rnd_b.rds")
saveRDS(m3.pss_flow_b, file = "m3.pss_flow_b.rds")

summary(m3.pss_flow_b)
tab_model(m3.pss_flow_b, show.se = 1, show.obs=1, show.ngroups=0)
```


2.4.1 Bayesian models comparison

```{r}
loo5<-LOO(m2.pss_session_b, reloo=1)
loo6<-LOO(m3.pss_prepost_b, reloo=1)
loo7<-LOO(m3.pss_condition_b, reloo=1)
loo8<-LOO(m3.pss_condition_rnd_b, reloo=1)
loo9<-LOO(m3.pss_flow_b, reloo=1)

loo::compare(loo5, loo6, loo7, loo8, loo9)
```


2.4.2 Histogram of posterior samples of M3b_PSS

```{r}
m3.pss_flow_b %>%
  plot( 
    combo = c("hist", "trace"), widths = c(1, 1.5),
  theme = theme_bw(base_size = 10)
)    

```


2.4.3 Figure of the effects of M3b_PSS

```{r}
# create df for plotting
summary_df_pss <- ggpredict(m3.pss_flow_b, c("cflow", "prepost"))

# define gray colors for the groups (pre; post)
colours <- c("Black","Black") # for greyscale: #a8a7a7; #383838

y<-ggplot(summary_df_pss,aes(x=x,y=predicted))+
  geom_line(aes(color=group,linetype=group),
            size=1.2)+ # change inner line size
  geom_ribbon(aes(ymin = summary_df_pss$conf.low, ymax = summary_df_pss$conf.high,fill = group,colour = group),labels = c("Pre", "Post"), linetype = 0,alpha = 0.07)+ # produces conf. ribbons
  labs(fill='Pre/Post') +
  labs(color='Pre/Post') +
  labs(linetype='Pre/Post')+
  scale_y_continuous(limits = c(0,100))+ # define y-axis limits
  scale_x_continuous(limits = c(-1.6,1.6))+
  theme_tufte(base_family = "GillSans")+ # make the plot tufte
  ylab("PSS")+ # y-axis label
  xlab("Flow")+ # x-axis label
  theme(axis.line = element_line(size = .5, color = "#969696"), # more plot aesthetics changes
        axis.ticks = element_line(color = "#969696"),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        text=element_text(size = 16),
        plot.title = element_text(size =18,
                                  hjust = 0.5),
        axis.title.y = element_text(vjust = 0.5,
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  scale_colour_manual(values=colours, labels = c("Pre", "Post")) + # apply defined colors
  scale_fill_manual(values=colours, labels = c("Pre", "Post"))

show(y)

ggsave("Figure-06.jpeg", plot = last_plot(), dpi = 900)
```


2.4.4 Plotting the differences of the estimated bayesian and frequentistic Model of the PSS

```{r}
Ploteffects_PSS <-Compare_Models_PSS %>% 
  select(lCI, uCI, Mean, Parameter=Parameters, Model)

apatheme=theme_bw()+  #Creating APA conform Theme  
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text=element_text(),
        legend.title=element_blank())

b <- ggplot() + 
  geom_errorbarh(data=Ploteffects_PSS, mapping=aes(y=Parameter, xmin=lCI, xmax=uCI, colour=Model, height=0.4)) +
  geom_point(data=Ploteffects_PSS, mapping=aes(y=Parameter, x=Mean, colour=Model), size=2)

Plott_dif_Models_PSS <- b + apatheme + geom_vline(xintercept = 0, linetype = "dotted") #Adding Theme and line on 0

show(Plott_dif_Models_PSS) 
```

